Attribute fusion in a latent process model for time series of graphs

### 2011-04-26 ssp2011.tex
Add discussion of fusion statistics for max degree

\usepackage[colon,sort&compress]{natbib}

@@

@@

  \mathrm{scan}_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K}
  \lambda_k \sum_{u,w \in N(v)} \mathbf{1}\{\phi(uw,t) = k\} \\

@@

  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{(u,v,w) \in
    \binom{V}{3}} h_k(u,v,w)

@@

of three vertices, forms a triangle (3-clique) of type $k$. A triangle

@@

Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6}) through
Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{m}_\lambda(t)$

@@

 \bar{J}^{m}_{\lambda}(t) = \frac{1}{m}\sum_{s = 1}^{m} J_{\lambda}(t - s) 

@@

where $m \in \mathbb{N}$ specified the width of the running-average

@@

statistic $T_{\lambda}^{m}(t)$ as defined by

@@

 T_{\lambda}^{m}(t) = % \begin{cases}

@@

     \bar{J}_{\lambda}^{m}(t)}{\sqrt{\tfrac{1}{m-1}
       \sum_{s=1}^{m}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{m}(t))^2}}

@@

for $m \geq 2$. 
\begin{theorem}
  \label{thm:1}
  Let $\lambda^{*}$ be the eigenvector corresponding to the largest
  eigenvalue of $ \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}$,
  i.e., 

@@

   \label{eq:9}
  \lambda^{*} = \argmax_{\lambda \colon \| \lambda \| = 1}
  \lambda^{T} \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}
  \lambda.

@@

 We then have
   \label{eq:8}
 \argmax_{\lambda \in \mathcal{B}}
 \mu_{\lambda} \, \cap \, \{\lambda^{*}, - \lambda^{*}\} \not = \emptyset \\
 \argmin_{\lambda \in \mathcal{B}} \mu_{\lambda} \, \cap \, \{\lambda^{*}, -
 \lambda^{*}\} \not = \emptyset.
\end{theorem}
\bibliography{ssp2011}
\end{document}

>>>>

%\usepackage[colon,sort&compress]{natbib}

@@

  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
    \binom{V}{3}} h_k(u,v,w) \\

@@

@@

  \Psi_{\lambda}(G(t)) = \max_{v \in V} \sum_{k = 1}^{K}
  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbf{1}\{\phi(uw,t) = k\} 

@@

of three vertices, forms a triangle of type $k$. A triangle

@@

Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6} through
Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{l}_\lambda(t)$

@@

 \bar{J}^{l}_{\lambda}(t) = \frac{1}{l}\sum_{s = 1}^{l} J_{\lambda}(t - s) 

@@

where $l \in \mathbb{N}$ specified the width of the running-average

@@

statistic $T_{\lambda}^{l}(t)$ as defined by

@@

 T_{\lambda}^{l}(t) = % \begin{cases}

@@

     \bar{J}_{\lambda}^{l}(t)}{\sqrt{\tfrac{1}{l-1}
       \sum_{s=1}^{l}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{l}(t))^2}}

@@

for $l \geq 2$. 
\begin{figure}[htbp]
  \centering
  \includegraphics[width=8cm]{graphics/Fig4-SSP2011.pdf}
  \caption{Temporal standardization: when testing for change at time $t$, the recent past (graphs $G(t - l), \dots, G(t-1)$ is used to standardize the invariants}
  \label{fig:temporal}
\end{figure}
It was shown in
\cite{lee:_laten_proces_model_time_attrib_random_graph} that when
$J_\lambda(t) = \mathrm{size}_{\lambda}(t)$, the normalized fusion
statistic $T_{\lambda}^{l}(t)$ follows a $t$-distribution with $l - 1$
degrees of freedom in the limit. Specifically, we have the following
results
\begin{lemma}
  \label{lem:1}
  Let $t \in \{l+1, \dots, t^{*}\}$ and $\lambda \in
  \mathbb{R}^{K}$. Define the vector $\zeta$ and the matrix $\xi$ by
    \zeta = \tbinom{m}{2}(\pi_{11} - \pi_{00}) + (n-m)m(\pi_{01} -
    \pi_{00}) \\
    \xi = (1+1/l)\tbinom{n}{2} \eta_{00} +
          \tbinom{m}{2}(\eta_{11} - \eta_{00}) + (n-m)m(\eta_{01} -
          \eta_{00})
As $n \rightarrow \infty$, the random variable
  $\psi^{l}_{\lambda}(t)$ converges weakly to the Student
  $t$-distribution with $l-1$ degrees of freedom and non-centrality
  parameter $\mu_{\lambda}$, where

@@

    \label{eq:10}
    \mu_{\lambda} = \begin{cases}
      \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} \\
      0 & \text{otherwise}
    \end{cases}

@@

\end{lemma}

\begin{theorem}
  \label{thm:1}
  Let $\lambda^{*}$ be the eigenvector corresponding to the largest
  eigenvalue of $ \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}$,
  i.e., 
 \begin{equation}
   \label{eq:9}
  \lambda^{*} = \argmax_{\lambda \colon \| \lambda \| = 1}
  \lambda^{T} \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}
  \lambda.
 \end{equation}
 We then have
 \begin{gather}
   \label{eq:8}
 \argmax_{ \|\lambda\| = 1}
 \mu_{\lambda} \, \cap \, \{\lambda^{*}, - \lambda^{*}\} \not = \emptyset \\
 \argmin_{ \| \lambda \| = 1} \mu_{\lambda} \, \cap \, \{\lambda^{*}, -
 \lambda^{*}\} \not = \emptyset.
 \end{gather}
\end{theorem}
\bibliography{ssp2011}
\end{document}
